```{r config, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}
# Run config first to use dynamic variables in the YAML
if (!require("upstartr")) install.packages("upstartr")
library("upstartr")
run_config()

```

---
title: "COVID-19 cases and vaccinations"
author: "Michael Pereira <michael.pereira@freepress.mb.ca>"
date: "`r format(Sys.Date(), "%B %d, %Y")`"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: textmate
    theme: simplex
    df_print: kable
    self_contained: false
    code_folding: hide
---


```{r config_session, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}

source(dir_src("theme.R"))
source(dir_src("palette.R"))


knit_print.data.frame = function(x, ...) {
  res = paste(c("", "", knitr::kable(x)), collapse = "\n")
  knitr::asis_output(res)
}

registerS3method(
  "knit_print", "data.frame", knit_print.data.frame,
  envir = asNamespace("knitr")
)

# This is normally set in the get.R file
Sys.sleep(time_pause)


```

```{r readin_json, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}


start <- as.Date("2020-09-14",format="%Y-%m-%d")
end <- as.Date("2021-05-28",format="%Y-%m-%d")
importJSON <- "Full" # None/Full

# THIS TAKES A FEW MINUTES, READ THE CSV UNLESS IT'S THE FIRST RUN OF THE DAY
# Create df based on what the JSON contains then rbind in the while loop

# Pull from JSON and stack the dates
# Oct 4 and 10 are wrong in this b/c column names
# change halfway through the month

if(importJSON == "Full"){

  theDate <- start

  demographics_df_sample <- jsonlite::fromJSON(dir_data_raw( "demographic_heatmap/2020-10-01-demographics-rha.json"))
  demographics_df_sample <- demographics_df_sample[["features"]][["attributes"]]
  demographics_df_sample <- demographics_df_sample %>%
    clean_names() %>%
    mutate(
      date = as.Date("2020-10-01", "%Y-%m-%d"),
      total_cases = NA,
      object_id = NA
    )
  demographics_df <- slice(demographics_df_sample, 0)
  # demographics_df <- demographics_df

  while (theDate <= end){

    file_name <- paste("/demographic_heatmap/", format(theDate,"%Y-%m-%d"), "-demographics-rha.json", sep="")
    print(file_name)

    demographics_rha_tmp <- jsonlite::fromJSON(dir_data_raw(file_name))

    # demographics_rha_tmp <- jsonlite::fromJSON(here::here(dir_data_raw, file_name))
    demographics_rha_tmp <- demographics_rha_tmp[["features"]][["attributes"]]
    demographics_rha_tmp <- demographics_rha_tmp %>%
      clean_names() %>%
      mutate(
        date = as.Date(theDate, "%Y-%m-%d")
      )

    if("total_cases" %in% colnames(demographics_rha_tmp)){
      demographics_rha_tmp <- demographics_rha_tmp %>% rename( value = total_cases )
    }

    if("object_id" %in% colnames(demographics_rha_tmp)){
      demographics_rha_tmp <- demographics_rha_tmp %>% select(-object_id)
    }

    demographics_df <- rbind(demographics_df, demographics_rha_tmp)

    Sys.sleep(.25)
    theDate <- theDate + 1

  }
  
  write_csv(demographics_df, dir_data_out(paste("demographics_df", '.csv', sep='')))

}
```

```{r get_read_data, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}

# Population estimates
MB_pop_estimates_2020_statcan_17_10_0005_01 <-  read_feather(dir_data_processed("MB_pop_estimates_2020_statcan_17_10_0005_01.feather"))

MB_pop_estimates_2020 <- MB_pop_estimates_2020_statcan_17_10_0005_01 %>%
  group_by(age_group_mb) %>%
  summarize(total = sum(population_2020est)) %>%
  mutate(
    age_group_mb = ifelse(age_group_mb == "100+", "99plus", age_group_mb),
    age_group_mb = ifelse(age_group_mb == "99+", "99plus", age_group_mb),    
  )


pop_99plus <- MB_pop_estimates_2020 %>% filter(age_group_mb == "99plus") %>% select(total) %>% pull()
pop_90_99 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "90-99") %>% select(total) %>% pull()
pop_80_89 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "80-89") %>% select(total) %>% pull()
pop_70_79 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "70-79") %>% select(total) %>% pull()
pop_60_69 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "60-69") %>% select(total) %>% pull()
pop_50_59 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "50-59") %>% select(total) %>% pull()
pop_40_49 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "40-49") %>% select(total) %>% pull()
pop_30_39 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "30-39") %>% select(total) %>% pull()
pop_20_29 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "20-29") %>% select(total) %>% pull()
pop_10_19 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "10-19") %>% select(total) %>% pull()
pop_0_9 <- MB_pop_estimates_2020 %>% filter(age_group_mb == "0-9") %>% select(total) %>% pull()
pop_90plus <- pop_99plus + pop_90_99


dashboard_demographics <- read_csv(dir_data_out("demographics_df.csv")) %>% 
    mutate(
      age_group = ifelse(age_group == "99+", "99plus", age_group),
      age_group = gsub("-", "_", age_group, fixed=TRUE)
    )

dashboard_demographics_allrha <- dashboard_demographics  %>%
  filter(rha == "All") %>%
  select(-rha) %>%
  pivot_wider(names_from = gender, values_from = value) %>%
  clean_names() %>%
  mutate(
    total_cases = male + female
  ) %>%
  select(
    -female, -male
  ) %>%
  pivot_wider(
    names_from="age_group",
    names_prefix = "age_",
    values_from="total_cases"
  ) %>% 
  mutate(
    daily_new_99plus = age_99plus - lag(age_99plus),
    daily_new_90_99  = age_90_99  - lag(age_90_99),
    daily_new_80_89  = age_80_89  - lag(age_80_89),
    daily_new_70_79  = age_70_79  - lag(age_70_79),
    daily_new_60_69  = age_60_69  - lag(age_60_69),
    daily_new_50_59  = age_50_59  - lag(age_50_59),
    daily_new_40_49  = age_40_49  - lag(age_40_49),
    daily_new_30_39  = age_30_39  - lag(age_30_39),
    daily_new_20_29  = age_20_29  - lag(age_20_29),
    daily_new_10_19  = age_10_19  - lag(age_10_19),
    daily_new_0_9    = age_0_9    - lag(age_0_9)
  )

dashboard_demographics_allrha__daily_new <- dashboard_demographics_allrha %>%  
  select(
    date,
    daily_new_99plus,
    daily_new_90_99,
    daily_new_80_89,
    daily_new_70_79,
    daily_new_60_69,
    daily_new_50_59,
    daily_new_40_49,
    daily_new_30_39,
    daily_new_20_29,
    daily_new_10_19,
    daily_new_0_9    
  ) %>% 
  mutate(
      daily_new_99plus = ifelse(is.na(daily_new_99plus), 0, daily_new_99plus),
      daily_new_90_99 = ifelse(is.na(daily_new_90_99), 0, daily_new_90_99), 
      daily_new_80_89 = ifelse(is.na(daily_new_80_89), 0, daily_new_80_89), 
      daily_new_70_79 = ifelse(is.na(daily_new_70_79), 0, daily_new_70_79), 
      daily_new_60_69 = ifelse(is.na(daily_new_60_69), 0, daily_new_60_69), 
      daily_new_50_59 = ifelse(is.na(daily_new_50_59), 0, daily_new_50_59), 
      daily_new_40_49 = ifelse(is.na(daily_new_40_49), 0, daily_new_40_49), 
      daily_new_30_39 = ifelse(is.na(daily_new_30_39), 0, daily_new_30_39), 
      daily_new_20_29 = ifelse(is.na(daily_new_20_29), 0, daily_new_20_29), 
      daily_new_10_19 = ifelse(is.na(daily_new_10_19), 0, daily_new_10_19), 
      daily_new_0_9 = ifelse(is.na(daily_new_0_9), 0, daily_new_0_9), 
  ) %>% 
  mutate(
    daily_new_90plus = daily_new_90_99 + daily_new_99plus
  )


dashboard_demographics_allrha__7day_new <- dashboard_demographics_allrha__daily_new %>% 
  mutate(
    new_cases_7day_avg_90plus = round(roll_mean(daily_new_90plus, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_99plus = round(roll_mean(daily_new_99plus, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_90_99 = round(roll_mean(daily_new_90_99, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_80_89 = round(roll_mean(daily_new_80_89, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_70_79 = round(roll_mean(daily_new_70_79, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_60_69 = round(roll_mean(daily_new_60_69, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_50_59 = round(roll_mean(daily_new_50_59, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_40_49 = round(roll_mean(daily_new_40_49, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_30_39 = round(roll_mean(daily_new_30_39, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_20_29 = round(roll_mean(daily_new_20_29, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_10_19 = round(roll_mean(daily_new_10_19, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_0_9 = round(roll_mean(daily_new_0_9, 7, na.rm=TRUE, fill=NA, align="right"), digits=1)
  ) %>% 
  select(
    date,
    new_cases_7day_avg_90plus,
    new_cases_7day_avg_99plus,
    new_cases_7day_avg_90_99,
    new_cases_7day_avg_80_89,
    new_cases_7day_avg_70_79,
    new_cases_7day_avg_60_69,
    new_cases_7day_avg_50_59,
    new_cases_7day_avg_40_49,
    new_cases_7day_avg_30_39,
    new_cases_7day_avg_20_29,
    new_cases_7day_avg_10_19,
    new_cases_7day_avg_0_9    
  )


dashboard_demographics_allrha__7day_new <- dashboard_demographics_allrha__daily_new %>% 
  mutate(
    new_cases_7day_avg_90plus = round(roll_mean(daily_new_90plus, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_99plus = round(roll_mean(daily_new_99plus, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_90_99 = round(roll_mean(daily_new_90_99, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_80_89 = round(roll_mean(daily_new_80_89, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_70_79 = round(roll_mean(daily_new_70_79, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_60_69 = round(roll_mean(daily_new_60_69, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_50_59 = round(roll_mean(daily_new_50_59, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_40_49 = round(roll_mean(daily_new_40_49, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_30_39 = round(roll_mean(daily_new_30_39, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_20_29 = round(roll_mean(daily_new_20_29, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_10_19 = round(roll_mean(daily_new_10_19, 7, na.rm=TRUE, fill=NA, align="right"), digits=1),
    new_cases_7day_avg_0_9 = round(roll_mean(daily_new_0_9, 7, na.rm=TRUE, fill=NA, align="right"), digits=1)
  ) %>% 
  select(
    date,
    new_cases_7day_avg_90plus,
    new_cases_7day_avg_99plus,
    new_cases_7day_avg_90_99,
    new_cases_7day_avg_80_89,
    new_cases_7day_avg_70_79,
    new_cases_7day_avg_60_69,
    new_cases_7day_avg_50_59,
    new_cases_7day_avg_40_49,
    new_cases_7day_avg_30_39,
    new_cases_7day_avg_20_29,
    new_cases_7day_avg_10_19,
    new_cases_7day_avg_0_9    
  )

dashboard_demographics_allrha__7day_new_100K <- dashboard_demographics_allrha__7day_new %>% 
  mutate(
    cases_100K_7day_avg_90plus = round(new_cases_7day_avg_90plus / pop_90plus * 100000, digits=1), 
    cases_100K_7day_avg_99plus = round(new_cases_7day_avg_99plus / pop_99plus * 100000, digits=1), 
    cases_100K_7day_avg_90_99 = round(new_cases_7day_avg_90_99 / pop_90_99 * 100000, digits=1), 
    cases_100K_7day_avg_80_89 = round(new_cases_7day_avg_80_89 / pop_80_89 * 100000, digits=1), 
    cases_100K_7day_avg_70_79 = round(new_cases_7day_avg_70_79 / pop_70_79 * 100000, digits=1), 
    cases_100K_7day_avg_60_69 = round(new_cases_7day_avg_60_69 / pop_60_69 * 100000, digits=1), 
    cases_100K_7day_avg_50_59 = round(new_cases_7day_avg_50_59 / pop_50_59 * 100000, digits=1), 
    cases_100K_7day_avg_40_49 = round(new_cases_7day_avg_40_49 / pop_40_49 * 100000, digits=1), 
    cases_100K_7day_avg_30_39 = round(new_cases_7day_avg_30_39 / pop_30_39 * 100000, digits=1), 
    cases_100K_7day_avg_20_29 = round(new_cases_7day_avg_20_29 / pop_20_29 * 100000, digits=1), 
    cases_100K_7day_avg_10_19 = round(new_cases_7day_avg_10_19 / pop_10_19 * 100000, digits=1), 
    cases_100K_7day_avg_0_9 = round(new_cases_7day_avg_0_9 / pop_0_9 * 100000, digits=1) 
  ) %>% 
  select(
    date,
    cases_100K_7day_avg_90plus,
    cases_100K_7day_avg_99plus,
    cases_100K_7day_avg_90_99,
    cases_100K_7day_avg_80_89,
    cases_100K_7day_avg_70_79,
    cases_100K_7day_avg_60_69,
    cases_100K_7day_avg_50_59,
    cases_100K_7day_avg_40_49,
    cases_100K_7day_avg_30_39,
    cases_100K_7day_avg_20_29,
    cases_100K_7day_avg_10_19,
    cases_100K_7day_avg_0_9    
  )


```



```{r viz_7day_cases_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

df_7day_cases_100K <- dashboard_demographics_allrha__7day_new_100K %>% 
  pivot_longer(
    cols=c(
      cases_100K_7day_avg_99plus,
      cases_100K_7day_avg_90plus,
      cases_100K_7day_avg_90_99,
      cases_100K_7day_avg_80_89,
      cases_100K_7day_avg_70_79,
      cases_100K_7day_avg_60_69,
      cases_100K_7day_avg_50_59,
      cases_100K_7day_avg_40_49,
      cases_100K_7day_avg_30_39,
      cases_100K_7day_avg_20_29,
      cases_100K_7day_avg_10_19,
      cases_100K_7day_avg_0_9
    ),
    names_to="age",
    values_to="cases_7day_100K"
  ) %>% 
  mutate(
    age = gsub("cases_100K_7day_avg_", "", age, fixed=TRUE)    
  ) %>% 
  filter(
    age %notin% c("99plus", "90_99")
  )


  p_7day_cases_100K <- ggplot(df_7day_cases_100K) + 
    aes(x = date, y = cases_7day_100K, colour=age, group=age) +
   
    annotate("segment", x = as.Date("2021-04-09"), xend = as.Date("2021-04-09"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-04-09"), y = 70, label = "60+", hjust=1.25) +
    
    annotate("segment", x = as.Date("2021-04-30"), xend = as.Date("2021-04-30"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-04-30"), y = 70, label = "50+", hjust=1.25) +
    
    annotate("segment", x = as.Date("2021-05-07"), xend = as.Date("2021-05-07"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-05-07"), y = 70, label = "40+", hjust=1.25) +

    annotate("segment", x = as.Date("2021-05-10"), xend = as.Date("2021-05-10"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-05-10"), y = 70, label = "30+", hjust=-.3) +

    geom_line(size = .75) +
 
    scale_x_date(
      expand = c(0, 0),
      limits = c(as.Date("2021-03-01"), as.Date("2021-06-15")),
      date_breaks = "2 weeks",
      labels = date_format("%b %d")
    ) +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, 80),
      labels = comma
      # labels = function(x) {
      #   ifelse(x %in% c(20), paste(x, "%", sep = ""), x)
      # }
    ) +  
    scale_color_hue() +
 labs(
    title = wrap_text("Daily COVID-19 cases per 100,000 people by age group", 70),
    subtitle = "Seven-day rolling average",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.2, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888"),
    strip.background=ggplot2::element_blank(),
    strip.text=ggplot2::element_text(size =13, hjust=0, face="bold"),
    panel.border=ggplot2::element_blank()
  )


wfp_7day_cases_100K <- prepare_plot(p_7day_cases_100K)
ggsave_pngpdf(wfp_7day_cases_100K, "wfp_7day_cases_100K", width_var = 8.66, height_var = 6, dpi_var=300, scale_var = 1, units_var = "in")

plot(wfp_7day_cases_100K)

```



```{r viz_7day_cases_100K_facet, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=14, results="asis", collapse = TRUE}

  p_7day_cases_100K_facet <- ggplot(df_7day_cases_100K) + 
    aes(x = date, y = cases_7day_100K, group=age) +
    

    annotate("segment", x = as.Date("2021-04-09"), xend = as.Date("2021-04-09"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-04-09"), y = 70, label = "60+", hjust=1.25) +
      
    annotate("segment", x = as.Date("2021-04-30"), xend = as.Date("2021-04-30"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-04-30"), y = 70, label = "50+", hjust=1.25) +
    
    annotate("segment", x = as.Date("2021-05-07"), xend = as.Date("2021-05-07"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-05-07"), y = 70, label = "40+", hjust=1.25) +

    annotate("segment", x = as.Date("2021-05-10"), xend = as.Date("2021-05-10"), 
             y = 0, yend = 80, colour = "#c9c9c9") +   
    annotate("text", x =as.Date("2021-05-10"), y = 70, label = "30+", hjust=-.3) +

    geom_line(size = .75, colour=wfp_blue) +

    # geom_text_repel(
    #   # geom_text(
    #     data=df_7day_cases_100K %>%  filter(date == max(date)),
    #     aes(x=date, y=cases_7day_100K,
    #         label=age
    #     ),
    #     color="#222222",
    #     force=10,
    #     size=4,
    #     hjust=-3,
    #     vjust=-.25,
    #     direction="y",
    #     segment.color="#c9c9c9",
    #     segment.size=.2,
    #     show.legend=FALSE
    #   ) +    
    scale_x_date(
      expand = c(0, 0),
      limits = c(as.Date("2021-03-01"), as.Date("2021-06-15")),
      date_breaks = "2 weeks",
      labels = date_format("%b %d")
    ) +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, 80),
      labels = comma
      # labels = function(x) {
      #   ifelse(x %in% c(20), paste(x, "%", sep = ""), x)
      # }
    ) +  
    scale_color_hue() +
    guides(colour=FALSE) +
 labs(
    title = wrap_text("Daily COVID-19 cases per 100,000 people by age group", 70),
    subtitle = "Seven-day rolling average",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.9, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888"),
    strip.background=ggplot2::element_blank(),
    strip.text=ggplot2::element_text(size =13, hjust=0, face="bold"),
    panel.border=ggplot2::element_blank()
  ) +
  facet_wrap(.~age, ncol = 2)


wfp_7day_cases_100K_facet <- prepare_plot(p_7day_cases_100K_facet)
ggsave_pngpdf(wfp_7day_cases_100K_facet, "wfp_7day_cases_100K_facet", width_var = 8.66, height_var = 14, dpi_var=300, scale_var = 1, units_var = "in")

plot(wfp_7day_cases_100K_facet)

```


## Data tables

### MB_pop_estimates_2020
```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(MB_pop_estimates_2020,
          caption = 'Table: MB_pop_estimates_2020',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 25,
            order = list(list(0, 'desc'))
          )
)
```

### dashboard_demographics_allrha__daily_new
```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(dashboard_demographics_allrha__daily_new,
          caption = 'Table: dashboard_demographics_allrha__daily_new',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 10,
            order = list(list(0, 'desc'))
          )
)
```

### dashboard_demographics_allrha__7day_new
```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(dashboard_demographics_allrha__7day_new,
          caption = 'Table: dashboard_demographics_allrha__7day_new',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 10,
            order = list(list(0, 'desc'))
          )
)

```

### dashboard_demographics_allrha__7day_new_100K
```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(dashboard_demographics_allrha__7day_new_100K,
          caption = 'Table: dashboard_demographics_allrha__7day_new_100K',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 10,
            order = list(list(0, 'desc'))
          )
)


```

