```{r config, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
# Run config first to use dynamic variables in the YAML
if (!require("upstartr")) install.packages("upstartr")
library("upstartr")
run_config()
```

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width = 8.66, fig.height = 6, fig.path = "graphics/", echo = FALSE, message = FALSE, warning = FALSE, collapse = TRUE)
```

---
title: "COVID-19 2nd and 3rd wave"
author: "Michael Pereira <michael.pereira@freepress.mb.ca>"
date: "`r format(Sys.Date(), "%B %d, %Y")`"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: textmate
    theme: cosmo
    df_print: kable
    self_contained: true
    css: style.css
    code_folding: hide
---


```{r get_read_data}

# Update timestamp
last_update_timestamp <- Sys.Date()
source(dir_src("theme.R"))
source(dir_src("palette.R"))

run_process()

run_analyze()
```

## Data import

### Dashboard
```{r compare_dashboard, class.source = 'fold-show'}

# Cases
dashboard_daily_status_all_2nd3rd <- dashboard_daily_status_all %>%
  filter(date >= "2020-09-04" & date <= "2021-04-20") %>%
  mutate(
    month = month(date),
    cases_mavg_7day = roll_mean(daily_cases, 7, na.rm = TRUE, fill = NA, align = "right"),
    cases_mavg_7day_100K = cases_mavg_7day / population_manitoba_2020 * 100000
  )

dashboard_daily_status_all_2nd_wave <- dashboard_daily_status_all_2nd3rd %>%
  mutate(month = month(date)) %>%
  filter(month == 10) %>%
  select(-rha, -object_id, -month)


dashboard_daily_status_all_3rd_wave <- dashboard_daily_status_all_2nd3rd %>%
  filter(date >= max(date) - 31) %>%
  select(-rha, -object_id)

cases_30day_2nd_wave_sum <- sum(dashboard_daily_status_all_2nd_wave$daily_cases)
cases_30day_2nd_wave_min <- min(dashboard_daily_status_all_2nd_wave$daily_cases)
cases_30day_2nd_wave_max <- max(dashboard_daily_status_all_2nd_wave$daily_cases)
cases_30day_2nd_wave_median <- median(dashboard_daily_status_all_2nd_wave$daily_cases)

cases_30day_3rd_wave_sum <- sum(dashboard_daily_status_all_3rd_wave$daily_cases)
cases_30day_3rd_wave_min <- min(dashboard_daily_status_all_3rd_wave$daily_cases)
cases_30day_3rd_wave_max <- max(dashboard_daily_status_all_3rd_wave$daily_cases)
cases_30day_3rd_wave_median <- median(dashboard_daily_status_all_3rd_wave$daily_cases)
```

### Bulletins
```{r compare_bulletins}

wfp_daily_bulletin <-
  wfp_daily_totals %>%
  select(
    date, new_daily_cases, active, recovered, deaths, total_hospital, total_icu,
    active_hospital, active_icu, test_to_date
  ) %>%
  filter(date >= "2020-09-04" & date <= "2021-04-20") %>%
  mutate(
    month = month(date),
    new_daily_mavg_7day = roll_mean(new_daily_cases, 7, na.rm = TRUE, fill = NA, align = "right"),
    hospitalizations_active_mavg_7day = roll_mean(active_hospital, 7, na.rm = TRUE, fill = NA, align = "right"),
    icu_active_mavg_7day = roll_mean(active_icu, 7, na.rm = TRUE, fill = NA, align = "right")
  ) %>%
  fill(active_hospital, active_icu)


wfp_daily_bulletin_2nd_wave <- wfp_daily_bulletin %>%
  mutate(month = month(date)) %>%
  filter(month == 10)

wfp_daily_bulletin_3rd_wave <- wfp_daily_bulletin %>%
  filter(date >= max(date) - 31)


hospitalizations_active_30day_2nd_wave_min <- min(wfp_daily_bulletin_2nd_wave$active_hospital)
hospitalizations_active_30day_2nd_wave_max <- max(wfp_daily_bulletin_2nd_wave$active_hospital)
hospitalizations_active_30day_2nd_wave_median <- median(wfp_daily_bulletin_2nd_wave$active_hospital)

hospitalizations_active_30day_3rd_wave_min <- min(wfp_daily_bulletin_3rd_wave$active_hospital)
hospitalizations_active_30day_3rd_wave_max <- max(wfp_daily_bulletin_3rd_wave$active_hospital)
hospitalizations_active_30day_3rd_wave_median <- median(wfp_daily_bulletin_3rd_wave$active_hospital)

icu_active_30day_2nd_wave_min <- min(wfp_daily_bulletin_2nd_wave$active_icu)
icu_active_30day_2nd_wave_max <- max(wfp_daily_bulletin_2nd_wave$active_icu)
icu_active_30day_2nd_wave_median <- median(wfp_daily_bulletin_2nd_wave$active_icu)

icu_active_30day_3rd_wave_min <- min(wfp_daily_bulletin_3rd_wave$active_icu)
icu_active_30day_3rd_wave_max <- max(wfp_daily_bulletin_3rd_wave$active_icu)
icu_active_30day_3rd_wave_median <- median(wfp_daily_bulletin_3rd_wave$active_icu)
```


### Five-day positivity
```{r compare_5day_positivity}

fiveday_positivity_2nd_3rd_wave <- dashboard_5day_positivity %>%
  filter(date >= "2020-09-04" & date <= "2021-04-20")

fiveday_positivity_2nd_wave <- fiveday_positivity_2nd_3rd_wave %>%
  mutate(month = month(date)) %>%
  filter(month == 10)

fiveday_positivity_3rd_wave <- fiveday_positivity_2nd_3rd_wave %>%
  filter(date >= max(date) - 31)
```

### Demographics
```{r compare_demographics_full_import}

start <- as.Date("2020-09-14",format="%Y-%m-%d")
end <- as.Date("2021-05-17",format="%Y-%m-%d")
importJSON <- "None" # None/Full

# THIS TAKES A FEW MINUTES, READ THE CSV UNLESS IT'S THE FIRST RUN OF THE DAY
# Create df based on what the JSON contains then rbind in the while loop

# Pull from JSON and stack the dates
# Oct 4 and 10 are wrong in this b/c column names
# change halfway through the month

if(importJSON == "Full"){
    
  theDate <- start
  
  demographics_df_sample <- jsonlite::fromJSON(dir_data_raw( "demographic_heatmap/2020-10-01-demographics-rha.json"))
  demographics_df_sample <- demographics_df_sample[["features"]][["attributes"]]
  demographics_df_sample <- demographics_df_sample %>%
    clean_names() %>%
    mutate(
      date = as.Date("2020-10-01", "%Y-%m-%d"),
      total_cases = NA,
      object_id = NA
    )
  demographics_df <- slice(demographics_df_sample, 0)
  # demographics_df <- demographics_df
  
  while (theDate <= end){
  
    file_name <- paste("/demographic_heatmap/", format(theDate,"%Y-%m-%d"), "-demographics-rha.json", sep="")
    print(file_name)
  
    demographics_rha_tmp <- jsonlite::fromJSON(dir_data_raw(file_name))
  
    # demographics_rha_tmp <- jsonlite::fromJSON(here::here(dir_data_raw, file_name))
    demographics_rha_tmp <- demographics_rha_tmp[["features"]][["attributes"]]
    demographics_rha_tmp <- demographics_rha_tmp %>%
      clean_names() %>%
      mutate(
        date = as.Date(theDate, "%Y-%m-%d")
      )
  
    if("total_cases" %in% colnames(demographics_rha_tmp)){
      demographics_rha_tmp <- demographics_rha_tmp %>% rename( value = total_cases )
    }
  
    if("object_id" %in% colnames(demographics_rha_tmp)){
      demographics_rha_tmp <- demographics_rha_tmp %>% select(-object_id)
    }
  
    demographics_df <- rbind(demographics_df, demographics_rha_tmp)
  
    Sys.sleep(.25)
    theDate <- theDate + 1
  
  }
  
  write_csv(demographics_df, dir_data_out(paste("demographics_df", '.csv', sep='')))  
    
}

dashboard_demographics <- read_csv(dir_data_out("demographics_df.csv"))

MB_pop_estimates_2020 <- MB_pop_estimates_2020_statcan_17_10_0005_01 %>%
  group_by(age_group_mb) %>%
  summarize(total = sum(population_2020est)) %>%
  mutate(
    age_group_mb = ifelse(age_group_mb == "100+", "99+", age_group_mb)
  )

dashboard_demographics_allrha <- read_csv(dir_data_out("demographics_df.csv")) %>%
  filter(rha == "All") %>%
  select(-rha) %>%
  pivot_wider(names_from = gender, values_from = value) %>%
  clean_names() %>%
  mutate(
    total_cases = male + female
  ) %>%
  left_join(
    MB_pop_estimates_2020,
    by = c("age_group" = "age_group_mb")
  ) %>%
  rename(
    population_2020est = total
  ) %>%
  mutate(
    cumulative_case_rate = total_cases / population_2020est * 100000
  )


dashboard_demographics_allrha_2nd_wave <- dashboard_demographics_allrha %>%
  mutate(month = month(date)) %>%
  filter(month == 10)

dashboard_demographics_allrha_3rd_wave <- dashboard_demographics_allrha %>%
  filter(date >= max(date) - 31)
```

## Key points

* Daily cases are sourced from dashboard data and show the test date. Investigation and reporting lags can lead to differences in counts between the dashboard dates and summary statistics as reported in the daily bulletin.

```{r keypoints}

cat(paste("\n\n#### Second wave (Oct. 2020)"))
cat(paste("\n*", "New daily cases:", "daily min:", comma(cases_30day_2nd_wave_min), " | median:", comma(cases_30day_2nd_wave_median), " | max:", comma(cases_30day_2nd_wave_max), " | total:", comma(cases_30day_2nd_wave_sum), sep = " "))
cat(paste("\n*", "Hospitalizations (active, incl ICU):", "daily min:", comma(hospitalizations_active_30day_2nd_wave_min), " | median:", comma(hospitalizations_active_30day_2nd_wave_median), " | max:", comma(hospitalizations_active_30day_2nd_wave_max), sep = " "))
cat(paste("\n*", "ICU (active): daily min:", comma(icu_active_30day_2nd_wave_min), " | median:", comma(icu_active_30day_2nd_wave_median), " | max:", comma(icu_active_30day_2nd_wave_max), sep = " "))

daysprior_31 <- max(dashboard_daily_status_all_3rd_wave$date) - 31
cat(paste("\n\n#### Third wave ", daysprior_31, "-", max(dashboard_daily_status_all_3rd_wave$date), "(31 days)"))
cat(paste("\n*", "New daily cases:", "daily min:", comma(cases_30day_3rd_wave_min), " | median:", comma(cases_30day_3rd_wave_median), " | max:", comma(cases_30day_3rd_wave_max), " | total:", comma(cases_30day_3rd_wave_sum), sep = " "))
cat(paste("\n*", "Hospitalizations (active, incl ICU): daily min:", comma(hospitalizations_active_30day_3rd_wave_min), " | median:", comma(hospitalizations_active_30day_3rd_wave_median), " | max:", comma(hospitalizations_active_30day_3rd_wave_max), sep = " "))
cat(paste("\n*", "ICU (active): daily min:", comma(icu_active_30day_3rd_wave_min), " | median:", comma(icu_active_30day_3rd_wave_median), " | max:", comma(icu_active_30day_3rd_wave_max), sep = " "))
```

## Graphics

### New daily cases

**Test date as noted in the dashboard data and may differ from numbers reported in the bulletin.**
```{r viz_cases_2nd_3rd, fig.width=8.66, fig.height=6}

p_2nd_3rd_wave_cases <- ggplot(dashboard_daily_status_all_2nd3rd) +
  aes(x = date, weight = daily_cases) +
  geom_bar(colour = "#e9e9e9", fill = "#e9e9e9", size = .5) +
  geom_bar(
    data = dashboard_daily_status_all_2nd_wave,
    aes(x = date, weight = daily_cases),
    colour = nominalMuted_shade_0, fill = nominalMuted_shade_0, size = .5
  ) +
  geom_bar(
    data = dashboard_daily_status_all_3rd_wave,
    aes(x = date, weight = daily_cases),
    colour = nominalMuted_shade_0, fill = nominalMuted_shade_0, size = .5
  ) +
  annotate("text",
    x = as.Date("2020-10-16"),
    y = 480,
    label = paste(comma(cases_30day_2nd_wave_sum), "\nnew cases", sep = ""),
    vjust = 0.8, size = 4, lineheight = 1,
    colour = "#000000"
  ) +
  annotate("text",
    x = as.Date("2021-04-04"),
    y = 440,
    label = paste(comma(cases_30day_3rd_wave_sum), "\nnew cases", sep = ""),
    vjust = 0.8, size = 4, lineheight = 1,
    colour = "#000000"
  ) +

  geom_curve(
    data = data.frame(
      x = as.Date("2020-10-12"), y = 410,
      xend = as.Date("2020-10-27"), yend = 90
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = .25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +
  geom_curve(
    data = data.frame(
      x = as.Date("2021-04-09"), y = 370,
      xend = as.Date("2021-04-08"), yend = 30
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = -0.25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +


  geom_line(aes(x = date, y = cases_mavg_7day),
           colour="#ffffff",size=1.2) +
  geom_line(aes(x = date, y = cases_mavg_7day),
           colour=nominalBold_shade_1,size=.8) +

  geom_text(data=dashboard_daily_status_all_2nd3rd %>% filter(date == max(date)),
          aes(x = date + 5, y = cases_mavg_7day - 1,
          label = wrap_text(paste("Seven-day moving average ", sep=""), 13)
        ),
          color="#000000", hjust = .05, vjust = 1, size=3
  ) +

  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-05-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 800),
    labels = scales::comma
  ) +
  labs(
    title = wrap_text("Daily cases of COVID-19 in Manitoba", 70),
    subtitle = wrap_text("Reported test date", 80),
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.9, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )

p_2nd_3rd_wave_cases <- prepare_plot(p_2nd_3rd_wave_cases)
ggsave_pngpdf(p_2nd_3rd_wave_cases, "p_2nd_3rd_wave_cases", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")

plot(p_2nd_3rd_wave_cases)
```





### Daily hospitalizations

**As reported in the daily bulletin and dashboard. Using active/contagious cases because that is what's available for October.**
```{r viz_hospitalizations_2nd_3rd, fig.width=8.66, fig.height=6}

p_2nd_3rd_wave_hospitalizations <- ggplot(wfp_daily_bulletin) +
  aes(x = date, weight = active_hospital) +

  geom_bar(colour = "#e9e9e9", fill = "#e9e9e9", size = .5) +
  # geom_line(aes(x = date, y = hospitalizations_active_mavg_7day),
  #          colour=nominalMuted_shade_1,size=1) +

  geom_bar(
    data = wfp_daily_bulletin_2nd_wave,
    aes(x = date, weight = active_hospital),
    colour = wfp_blue, fill = wfp_blue, size = .5
  ) +

  geom_bar(
    data = wfp_daily_bulletin_2nd_wave,
    aes(x = date, weight = active_hospital),
    colour = wfp_blue, fill = wfp_blue, size = .5
  ) +
  geom_bar(
    data = wfp_daily_bulletin_3rd_wave,
    aes(x = date, weight = active_hospital),
    colour = wfp_blue, fill = wfp_blue, size = .5
  ) +

  # geom_text(data=wfp_daily_bulletin_2nd_wave %>% filter(date==max(date)),
  #           aes(x = date, y = active_hospital,
  #               label=paste(format(date, "%b %d"), "\n", active_hospital, sep="")
  #               ),
  #           colour="#000000", size=4, vjust=-.75) +
  # geom_text(data=wfp_daily_bulletin_3rd_wave %>% filter(date==max(date)),
  #           aes(x = date, y = active_hospital,
  #               label=paste(format(date, "%b %d"), "\n", active_hospital, sep="")
  #               ),
  #           colour="#000000", size=4, vjust=-.75) +

  annotate("text",
    x = as.Date("2020-10-17"),
    y = 190,
    label = paste("Median of ", comma(hospitalizations_active_30day_2nd_wave_median), "\nactive cases\n in hospital", sep = ""),
    vjust = 0.8, size = 4,
    colour = "#000000"
  ) +
  annotate("text",
    x = as.Date("2021-04-04"),
    y = 250,
    label = paste("Median of ", comma(hospitalizations_active_30day_3rd_wave_median), "\nactive cases\n in hospital", sep = ""),
    vjust = 0.8, size = 4,
    colour = "#000000"
  ) +
  geom_curve(
    data = data.frame(
      x = as.Date("2020-10-15"), y = 130,
      xend = as.Date("2020-10-15"), yend = 50
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = .25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +
  geom_curve(
    data = data.frame(
      x = as.Date("2021-04-04"), y = 190,
      xend = as.Date("2021-04-04"), yend = 80
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = -0.25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +
  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-04-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 400),
    labels = scales::comma
  ) +
  labs(
    title = wrap_text("Daily COVID-19 hospitalizations in Manitoba", 70),
    subtitle = "Active and contagious cases",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.9, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )


p_2nd_3rd_wave_hospitalizations <- prepare_plot(p_2nd_3rd_wave_hospitalizations)
ggsave_pngpdf(p_2nd_3rd_wave_hospitalizations, "p_2nd_3rd_wave_hospitalizations", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")

plot(p_2nd_3rd_wave_hospitalizations)
```


### Daily ICU hospitalizations

**As reported in the daily bulletin and dashboard. Using active/contagious cases because that is what's available for October.**
```{r viz_icu_2nd_3rd, fig.width=8.66, fig.height=6}

p_2nd_3rd_wave_icu <- ggplot(wfp_daily_bulletin) +
  aes(x = date, weight = active_icu) +
  geom_bar(colour = "#e9e9e9", fill = "#e9e9e9", size = .5) +
  # geom_line(aes(x = date, y = active_icu),
  #          colour=nominalMuted_shade_1,size=1) +

  geom_bar(
    data = wfp_daily_bulletin_2nd_wave,
    aes(x = date, weight = active_icu),
    colour = wfp_blue, fill = wfp_blue, size = .5
  ) +
  # geom_line(data=wfp_daily_bulletin_2nd_wave,
  #           aes(x = date, y = active_icu),
  #          colour=nominalBold_shade_1,size=1) +

  geom_bar(
    data = wfp_daily_bulletin_3rd_wave,
    aes(x = date, weight = active_icu),
    colour = wfp_blue, fill = wfp_blue, size = .5
  ) +
  # geom_line(data=wfp_daily_bulletin_3rd_wave,
  #           aes(x = date, y = active_icu),
  #          colour=nominalBold_shade_1,size=1) +

  # geom_text(data=wfp_daily_bulletin_2nd_wave %>% filter(date==max(date)),
  #           aes(x = date, y = active_icu,
  #               label=paste(format(date, "%b %d"), "\n", active_icu, sep="")
  #               ),
  #           colour="#000000", size=4, vjust=-.75) +
  # geom_text(data=wfp_daily_bulletin_3rd_wave %>% filter(date==max(date)),
  #           aes(x = date, y = active_icu,
  #               label=paste(format(date, "%b %d"), "\n", active_icu, sep="")
  #               ),
  #           colour="#000000", size=4, vjust=-.75) +
  annotate("text",
    x = as.Date("2020-10-16"),
    y = 40,
    label = paste("Median of ", comma(icu_active_30day_2nd_wave_median), "\nactive cases\n in ICU", sep = ""),
    vjust = 0.8, size = 4,
    colour = "#000000"
  ) +
  annotate("text",
    x = as.Date("2021-04-04"),
    y = 60,
    label = paste("Median of ", comma(icu_active_30day_3rd_wave_median), "\nactive cases\n in ICU", sep = ""),
    vjust = 0.8, size = 4,
    colour = "#000000"
  ) +
  geom_curve(
    data = data.frame(
      x = as.Date("2020-10-12"), y = 28,
      xend = as.Date("2020-10-15"), yend = 10
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = .25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +
  geom_curve(
    data = data.frame(
      x = as.Date("2021-04-06"), y = 48,
      xend = as.Date("2021-04-04"), yend = 16
    ),
    mapping = aes(x = x, y = y, xend = xend, yend = yend),
    size = .25, colour = "#000000", curvature = -0.25, arrow = structure(list(angle = 30, length = structure(0.1, class = "unit", valid.unit = 2L, unit = "inches"), ends = 2L, type = 2L), class = "arrow"), inherit.aes = FALSE, show.legend = FALSE
  ) +


  #   annotate("text",
  #        x = as.Date("2020-10-31"),
  #        y = 350,
  #        label = paste("Median of ", comma(icu_active_30day_2nd_wave_median), " active cases\n in ICU", sep=""),
  #        vjust = 0.8, size=4,
  #        colour = "#000000"
  # ) +
  #
  # annotate("text",
  #        x = as.Date("2021-03-15"),
  #        y = 350,
  #        label = paste("Median ", comma(icu_active_30day_3rd_wave_median), " active cases\n in ICU", sep=""),
  #        vjust = 0.8, size=4,
  #        colour = "#000000"
  # ) +
  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-04-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 80),
    labels = scales::comma
  ) +
  labs(
    title = wrap_text("Daily COVID-19 ICU hospitalizations in Manitoba", 70),
    subtitle = "Active and contagious cases",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.9, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )

p_2nd_3rd_wave_icu <- prepare_plot(p_2nd_3rd_wave_icu)
ggsave_pngpdf(p_2nd_3rd_wave_icu, "p_2nd_3rd_wave_icu", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")

plot(p_2nd_3rd_wave_icu)
```


### Five-day test positivity

**As reported in the daily bulletin and dashboard. The province wasn't consistently reporting Winnipeg's rate until Nov. 1, 2020.**
```{r viz_5day_test_positivity, fig.width=8.66, fig.height=6}

p_2nd_3rd_wave_positivity <- ggplot(fiveday_positivity_2nd_3rd_wave) +
  aes(x = date, y = positivity_rate_5day_mb) +
  geom_line(colour = "#c9c9c9", fill = "#c9c9c9", size = .75) +
  geom_line(
    data = fiveday_positivity_2nd_wave,
    aes(x = date, y = positivity_rate_5day_mb),
    colour = wfp_blue, size = 1
  ) +
  geom_line(
    data = fiveday_positivity_3rd_wave,
    aes(x = date, y = positivity_rate_5day_mb),
    colour = wfp_blue, size = 1
  ) +
  geom_point(
    data = fiveday_positivity_2nd_wave %>% filter(date == max(date)),
    aes(x = date, y = positivity_rate_5day_mb),
    colour = wfp_blue, size = 2.5
  ) +
  geom_point(
    data = fiveday_positivity_3rd_wave %>% filter(date == max(date)),
    aes(x = date, y = positivity_rate_5day_mb),
    colour = wfp_blue, size = 2.5
  ) +
  geom_text(
    data = fiveday_positivity_2nd_wave %>% filter(date == max(date)),
    aes(
      x = date, y = positivity_rate_5day_mb,
      label = paste(format(date, "%b %d"), "\n", positivity_rate_5day_mb, "%", sep = "")
    ),
    colour = "#000000", size = 4, vjust = -.75
  ) +
  geom_text(
    data = fiveday_positivity_3rd_wave %>% filter(date == max(date)),
    aes(
      x = date, y = positivity_rate_5day_mb,
      label = paste(format(date, "%b %d"), "\n", positivity_rate_5day_mb, "%", sep = "")
    ),
    colour = "#000000", size = 4, vjust = 2
  ) +
  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-04-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    labels = function(x) {
      ifelse(x %in% c(20), paste(x, "%", sep = ""), x)
    }
  ) +
  labs(
    title = wrap_text("Five-day test positivity for COVID-19 in Manitoba", 70),
    subtitle = "",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    fill = ""
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.9, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )

p_2nd_3rd_wave_positivity <- prepare_plot(p_2nd_3rd_wave_positivity)
ggsave_pngpdf(p_2nd_3rd_wave_positivity, "p_2nd_3rd_wave_positivity", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")

plot(p_2nd_3rd_wave_positivity)
```



### Case demographics


```{r viz_ct_chg_cases_age, fig.width=8.66, fig.height=6}

dashboard_demographics_allrha_jan1 <- dashboard_demographics_allrha %>% 
  filter(date == as.Date("2021-01-01")) %>% 
  select(
    date, age_group, total_cases
  )

dashboard_demographics_allrha_apr30 <- dashboard_demographics_allrha %>% 
  filter(date == max(date)) %>% 
  select(
    date, age_group, total_cases
  )

dashboard_demographics_allrha_jan1_apr30 <-  left_join(
  dashboard_demographics_allrha_jan1,
  dashboard_demographics_allrha_apr30,
  by=c("age_group"="age_group")
) %>% 
  rename(
    total_cases_jan1 = total_cases.x,
    total_cases_ytd = total_cases.y
  ) %>% 
  mutate(
    newcases_ytd = total_cases_ytd - total_cases_jan1,
    pct_chg = (total_cases_ytd - total_cases_jan1) / abs(total_cases_jan1) * 100
  ) %>% 
  select(
    -date.y
  )


```



**As reported in the dashboard data.**
```{r viz_case_demographics, fig.width=8.66, fig.height=6}

p_2nd_3rd_case_demographics <- ggplot(dashboard_demographics_allrha) +
  aes(x = date, y = total_cases, group = age_group) +
  geom_line(size = 1, alpha = .5, colour = "#c9c9c9") +
  geom_line(data=dashboard_demographics_allrha %>% filter(date >= as.Date("2021-01-01")) %>% filter(age_group %in% c("0-9", "10-19")),
            size = 1, alpha = 1, colour = wfp_blue) +
  # geom_line(
  #   data = dashboard_demographics_allrha_2nd_wave %>% filter(age_group %in% c("0-9", "10-19")),
  #   aes(x = date, y = total_cases, group = age_group),
  #   size = 1, alpha = 1, colour = wfp_blue
  # ) +
  # geom_line(
  #   data = dashboard_demographics_allrha_3rd_wave %>% filter(age_group %in% c("0-9", "10-19")),
  #   aes(x = date, y = total_cases, group = age_group),
  #   size = 1, alpha = 1, colour = wfp_blue
  # ) +
  geom_text_repel(
    data = dashboard_demographics_allrha %>% filter(date == max(date)),
    aes(x = date, y = total_cases,
        label = paste(age_group, ":", comma(total_cases, accuracy=1), sep=" "),
        fontface=ifelse(age_group %in% c("0-9", "10-19"), "bold", "plain")
        ),
    size = 4, colour = "#000000",
    hjust = -.5,
    color = "#222222",
    force=10,
    direction = "y",
    segment.color = "#999999",
    segment.size = .2,
    show.legend = FALSE

  ) +
  
  # annotate("text",
  #          x=as.Date("2021-01-24"),
  #          y=7200,
  #          label=wrap_text("Between Jan. 1 and May 8, cases among 0-9 year olds increased by 138 per cent. Among 10-19 year olds, cases grew by 92 per cent in the same four month period.", 42),
  #          hjust=1, vjust=0.8, size=4,
  #          colour="#000000"
  # ) +
  # 
  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-08-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 10000),
    label=comma
    # ,
    # labels = function(x) { ifelse(x %in% c(20), paste(x, "%", sep = ""), x) }
  ) +
  labs(
    title = wrap_text("Reported cases of COVID-19 in Manitoba by age group", 70),
    subtitle= wrap_text("All cases to date", 80),
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    colour = "Age group"
  ) +
  minimal_theme() +
  theme(
      # plot.title = ggplot2::element_text(margin=ggplot2::margin(0,0,20,0)),
    legend.position = c(.2, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )

p_2nd_3rd_case_demographics <- prepare_plot(p_2nd_3rd_case_demographics)
ggsave_pngpdf(p_2nd_3rd_case_demographics, "p_2nd_3rd_case_demographics", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")

plot(p_2nd_3rd_case_demographics)
```


**As reported in the dashboard data.**
```{r viz_case_demographics_rate, fig.width=8.66, fig.height=6}


p_2nd_3rd_case_demographics_rate <- ggplot(dashboard_demographics_allrha) +
  aes(x = date, y = cumulative_case_rate, group = age_group) +
  geom_line(size = 1, alpha = .5, colour = "#c9c9c9") +
  geom_line(data=dashboard_demographics_allrha %>% filter(age_group %in% c("0-9", "10-19")),
            size = 1, alpha = 1, colour = wfp_blue) +

  #
  # geom_line(
  #   data = dashboard_demographics_allrha_2nd_wave %>% filter(age_group %in% c("0-9", "10-19")),
  #   aes(x = date, y = cumulative_case_rate, group = age_group),
  #   size = 1, alpha = 1, colour = wfp_blue
  # ) +
  # geom_line(
  #   data = dashboard_demographics_allrha_3rd_wave %>% filter(age_group %in% c("0-9", "10-19")),
  #   aes(x = date, y = cumulative_case_rate, group = age_group),
  #   size = 1, alpha = 1, colour = wfp_blue
  # ) +
  geom_text_repel(
    data = dashboard_demographics_allrha %>% filter(date == max(date)),
    aes(x = date, y = cumulative_case_rate,
        label = paste(age_group, ":", comma(cumulative_case_rate), sep=" "),
        fontface=ifelse(age_group %in% c("0-9", "10-19"), "bold", "plain")
        ),
    size = 4, colour = "#000000",
    hjust = -.5,
    color = "#222222",
    force=10,
    direction = "y",
    segment.color = "#999999",
    segment.size = .2,
    show.legend = FALSE

  ) +
  scale_x_date(
    expand = c(0, 0),
    limits = c(as.Date("2020-09-15"), as.Date("2021-08-30")),
    date_breaks = "1 month",
    labels = date_format("%b")
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 15000),
    label=comma
    # ,
    # labels = function(x) { ifelse(x %in% c(20), paste(x, "%", sep = ""), x) }
  ) +
  labs(
    title = wrap_text("Reported cases per capita of COVID-19 in Manitoba by age group", 70),
    subtitle="Cases per 100,000 people",
    caption = wrap_text(toupper(paste("WINNIPEG FREE PRESS — SOURCE: Manitoba Health (", last_update_timestamp, ")", sep = "")), 80),
    x = "",
    y = "",
    colour = "Age group"
  ) +
  minimal_theme() +
  theme(
    legend.position = c(.2, 1),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(10, 10, 10, 10),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    panel.grid.minor.x = ggplot2::element_blank(),
    panel.grid.minor.y = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_line(color="#888888")
  )

p_2nd_3rd_case_demographics_rate <- prepare_plot(p_2nd_3rd_case_demographics_rate)
ggsave_pngpdf(p_2nd_3rd_case_demographics_rate, "p_2nd_3rd_case_demographics_rate", width_var = 8.66, height_var = 6, dpi_var=96, scale_var = 1, units_var = "in")


plot(p_2nd_3rd_case_demographics_rate)
```



## Data tables

### 2nd wave - October 2020
#### Dashboard data
```{r table_2nd_3rd_oct_dashboard_cases, results="show"}

datatable(dashboard_daily_status_all_2nd_wave,
  caption = "Table: dashboard_daily_status_all_2nd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```

### 2nd wave - October 2020
#### Bulletin numbers
```{r table_2nd_3rd_oct_bulletin_cases, results="show"}

datatable(wfp_daily_bulletin_2nd_wave,
  caption = "Table: wfp_daily_bulletin_2nd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```


### 2nd wave - October 2020
#### Five-day test positivity
```{r table_2nd_3rd_oct_positivity, results="show"}

datatable(fiveday_positivity_2nd_wave,
  caption = "Table: fiveday_positivity_2nd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```

### 3rd wave - April 2021
#### Dashboard data
```{r table_2nd_3rd_april_dashboard_cases, results="show"}

datatable(dashboard_daily_status_all_3rd_wave,
  caption = "Table: dashboard_daily_status_all_3rd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```

### 3rd wave - April 2021
#### Bulletin numbers
```{r table_2nd_3rd_april_bulletin_cases, results="show"}

datatable(wfp_daily_bulletin_3rd_wave,
  caption = "Table: wfp_daily_bulletin_3rd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```

### 3rd wave - April 2021
#### Five-day test positivity
```{r table_2nd_3rd_april_positivity, results="show"}

datatable(fiveday_positivity_3rd_wave,
  caption = "Table: fiveday_positivity_3rd_wave",
  class = "cell-border stripe", rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(0, "desc"))
  )
)
```
