---
output: 
  html_document: 
    toc: yes
    highlight: textmate
    theme: flatly
    df_print: kable
---
```{r config, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
# Run config first to use dynamic variables in the YAML
if (!require("upstartr")) install.packages("upstartr")
library("upstartr")
run_config()
```
## Daily This Just In

Update the TJI worksheet on this Google Sheet
[https://docs.google.com/spreadsheets/d/19IqfhdXQaQbCJDns3yG0EEL4TAYGRgEGKKyLeELvLNA/edit#gid=362680117](TJI worksheet)

Use one `death_bullet` for the provided details of each reported COVID-19 death. 

Find/Replace to remove the hashmarks and check the final copy, it's a mixed bag of data feeds and manual entry. 


```{r prep_tji, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}
source(dir_src("tji.R"))
```

```{r show_tji, results="as-is", collapse = TRUE}
cat(tji_hed_body)
```

----------

```{r get_read_data, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}

source(dir_src("theme.R"))
source(dir_src("palette.R"))
source(dir_src("get.R"))

run_process()
run_analyze()
run_visualize()


# source(dir_src("insights.R"))

```


## Daily COVID-19 data

### Daily case status of reported COVID-19 in Manitoba
```{r viz_daily_case_status, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_daily_case_status.png
plot(wfp_daily_case_status)

```


### New daily and seven-day average cases of COVID-19 reported in Manitoba
```{r viz_wfp_new_daily_cases_avg, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_new_daily_cases_avg.png
plot(wfp_new_daily_cases_avg)
```


### Hospitalizations and ICU patients
```{r viz_wfp_daily_hospitalization, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_daily_hospitalization.png
plot(wfp_daily_hospitalization)
```



### New daily cases of COVID-19 per capita reported in Manitoba
```{r viz_wfp_new_daily_cases_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_new_daily_cases_100K.png
plot(wfp_new_daily_cases_100K)
```


### Reported cases of COVID-19 per capita reported in Manitoba
```{r viz_wfp_rha_total_cases_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_rha_total_cases_100K.png
plot(wfp_rha_total_cases_100K)
```


### Active cases of COVID-19 reported in Manitoba
```{r viz_wfp_rha_active_cases, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_rha_active_cases.png
plot(wfp_rha_active_cases)
```


### Active cases of COVID-19 per capita reported in Manitoba
```{r viz_wfp_rha_active_cases_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_rha_active_cases_100K.png
plot(wfp_rha_active_cases_100K)
```


### Five-day test positivity
```{r viz_wfp_5day_test_positivity, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_5day_test_positivity.png
plot(wfp_5day_test_positivity)
```


### COVID-19 deaths
```{r viz_wfp_mb_deaths, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_mb_deaths.png
plot(wfp_mb_deaths)
```

## Provincial COVID-19 comparisons

### COVID-19 cases per capita across Canada
```{r viz_wfp_phac_total_cases_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_phac_total_cases_100K.png
plot(wfp_phac_total_cases_100K)
```

### COVID-19 deaths per capita across Canada
```{r viz_wfp_phac_total_deaths_100K, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_phac_total_deaths_100K.png
plot(wfp_phac_total_deaths_100K)
```

### Growth in provincial cases since the tenth case
```{r viz_wfp_provincial_growth_timeline_since10, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_provincial_growth_timeline_since10.png
plot(wfp_provincial_growth_timeline_since10)
```

### COVID-19 variants
```{r viz_wfp_covid19_variants, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_covid19_variants.png
plot(wfp_covid19_variants)
```


## Vaccinations


### First and second vaccine doses
```{r viz_wfp_covid_19_mb_vaccinations_first_second, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_covid_19_mb_vaccinations_first_second.png
plot(wfp_covid_19_mb_vaccinations_first_second)
```

### Vaccinations -- age of those vaccinated
```{r viz_wfp_covid19_vaccine_demographics, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_covid19_vaccine_demographics.png
plot(wfp_covid19_vaccine_demographics)
```

### Vaccinations -- delivered and administered
```{r viz_wfp_vaccine_gap, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_vaccine_gap.png
plot(wfp_vaccine_gap)
```

### Vaccinations -- provincial comparison of doses administered
```{r viz_wfp_vaccine_gap_provinces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis"}
# wfp_vaccine_gap_provinces.png
plot(wfp_vaccine_gap_provinces)
```

## Weekly COVID-19 data



## Misc one-off COVID-19 data


