```{r config, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}
# Run config first to use dynamic variables in the YAML
if (!require("upstartr")) install.packages("upstartr")
library("upstartr")
run_config()

```

---
title: "COVID-19 vaccinations"
author: "Michael Pereira <michael.pereira@freepress.mb.ca>"
date: "`r format(Sys.Date(), "%B %d, %Y")`"
output:
  html_document:
    toc: true
    toc_float: true
    highlight: textmate
    theme: cosmo
    df_print: kable
    self_contained: false
    css: style.css
    code_folding: true
---


```{r get_read_data, echo=FALSE, message=FALSE, warning=FALSE, results="hide", collapse = TRUE}

source(dir_src("theme.R"))
source(dir_src("palette.R"))


knit_print.data.frame = function(x, ...) {
  res = paste(c("", "", knitr::kable(x)), collapse = "\n")
  knitr::asis_output(res)
}

registerS3method(
  "knit_print", "data.frame", knit_print.data.frame,
  envir = asNamespace("knitr")
)

# This is normally set in the get.R file
Sys.sleep(time_pause)


source(dir_src("get_vaccinations.R"))
source(dir_src("process.R"))
source(dir_src("process_vaccinations.R"))
run_analyze()

source(dir_src("visualize_strings.R"))
################################################################################
# Vaccinations
################################################################################
source(dir_src("visualize_vaccine_admin_gap.R"))
source(dir_src("visualize_vaccine_daily_vaccinations.R"))
source(dir_src("visualize_vaccine_demographic_coverage.R"))
source(dir_src("visualize_vaccine_targets.R"))


source(dir_src("visualize_vaccine_demographics.R"))
source(dir_src("visualize_vaccine_distribution.R"))
source(dir_src("visualize_vaccine_first_second_dose.R"))
source(dir_src("visualize_vaccine_gap_provinces.R"))

source(dir_src("_vaccination_comparison.R"))

# source(dir_src("_scratch", "visualize_vaccine_demographics_female_male.R"))
# source(dir_src("_scratch", "visualize_vaccine_distribution.R"))
# source(dir_src("_scratch", "visualize_vaccine_administration.R"))


```







----


## Daily vaccinations
### First, second and combined
```{r viz_wfp_covid_19_mb_daily_vaccinations_1st2nd, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_covid_19_mb_daily_vaccinations_1st2nd)

plot(wfp_covid_19_mb_daily_vaccinations_combined)

```


## Administered and unused doses of COVID-19 vaccine
### Admin gap
```{r viz_wfp_vaccine_gap, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_vaccine_gap)
```


## Vaccination demographic coverage
```{r viz_wfp_covid19_vaccine_demographics_coverage, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
plot(wfp_covid19_vaccine_demographics_coverage)
```


## Vaccination targets
### With seven-day average and daily outputs
```{r viz_wfp_vaccine_targets, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}
# plot(wfp_vaccine_targets)

plot(wfp_vaccine_targets_7dayavg)
```



## Provincial vaccine gaps
```{r viz_wfp_vaccine_gap_provinces, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

plot(wfp_vaccine_gap_provinces)
```



## Provincial comparison of unused doses per capita
```{r viz_wfp_admin_gap_comparison, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

plot(wfp_admin_gap_comparison)
```



----

## Provincial vaccine distribution, admin and admin gap and averages

```{r table_vaccine_compare_j_pop, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="hide", collapse = TRUE}

```

----

```{r work_vaccine_distribution_admin_admingap, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6}

# Load vaccine distribution & administration counts
# * standardize province names in to join with population
vaccine_compare <- covid_vaccine %>%
  mutate(
    province = ifelse(province == "BC", "British Columbia",
               ifelse(province == "NL", "Newfoundland and Labrador",
               ifelse(province == "NWT", "Northwest Territories",
               ifelse(province == "PEI", "Prince Edward Island",
                  province
               ))))
  )
# %>%
#   filter(date < max(date))


# Split out MB and update with latest and rebind rows
vaccine_compare_noMB <- vaccine_compare %>%
  filter(province != "Manitoba")

vaccine_compare_MB <- vaccine_compare %>%
  filter(province == "Manitoba")
# %>%
  # mutate(
  #   # cumulative_dvaccine = ifelse(date == max(date), 409470, cumulative_dvaccine),
  #   cumulative_avaccine = ifelse(date == max(date), 231049, cumulative_avaccine)
  # )

vaccine_compare <- rbind(
  vaccine_compare_noMB,
  vaccine_compare_MB
)

# Recast to dataframes for tidy join
vaccine_compare <-  as.data.frame(vaccine_compare)
population_provinces_18plus_2021Q2 <- as.data.frame(population_provinces_18plus_2021Q2)


# Join vaccination and population dataframes and calculate rates, etc.
provincial_vaccine_comparisons <- left_join(
    vaccine_compare,
    population_provinces_18plus_2021Q2,
    by=c("province"="province")
  ) %>%
  mutate(
    administered_doses_per_capita = cumulative_avaccine / population * 100000,
    administration_gap_per_capita = dose_difference / population * 100000
  ) %>%
  rename(
    dose_difference_cnt = dose_difference,
    vaccination_gap_pct = vaccination_gap
  ) %>%
  select(
    "date",
    "province",
    "population",
    # "dvaccine",
    "cumulative_dvaccine" ,
    # "avaccine",
    "cumulative_avaccine" ,
    "vaccination_gap_pct",
    "dose_difference_cnt" ,
    "administered_doses_per_capita",
    "administration_gap_per_capita"
  ) %>%
  filter(province %notin% c("Northwest Territories", "Nunavut", "Yukon"))

# Complete provincial_vaccine_comparisons table shown at bottom
```


```{r echo=TRUE, message=TRUE, warning=TRUE, fig.width=8.66, fig.height=6}

# Grab the most recent date of data
provincial_vaccine_comparisons_last_date <- provincial_vaccine_comparisons %>%
  filter(date==max(date)) %>%
  arrange(desc(administered_doses_per_capita)) %>%
  mutate(province = factor(province, unique(province))) # reset your factor-column based on that order


datatable(provincial_vaccine_comparisons_last_date,
          caption = 'Table: provincial_vaccine_comparisons_last_date',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 25,
            order = list(list(1, 'desc'))
          )
        )


```

```{r echo=TRUE, message=TRUE, warning=TRUE, fig.width=8.66, fig.height=6}

# calculate min, max and averages (mean and median)
min_administered_doses_per_capita <- min(provincial_vaccine_comparisons_last_date$administered_doses_per_capita)

cat(paste("Min: ", min_administered_doses_per_capita))

```

```{r echo=TRUE, message=TRUE, warning=TRUE, fig.width=8.66, fig.height=6}

max_administered_doses_per_capita <- min(provincial_vaccine_comparisons_last_date$administered_doses_per_capita)

cat(paste("Max: ", max_administered_doses_per_capita))

```

```{r echo=TRUE, message=TRUE, warning=TRUE, fig.width=8.66, fig.height=6}

median_administered_doses_per_capita <- median(provincial_vaccine_comparisons_last_date$administered_doses_per_capita)

cat(paste("Median: ", median_administered_doses_per_capita))

```

```{r echo=TRUE, message=TRUE, warning=TRUE, fig.width=8.66, fig.height=6}

mean_administered_doses_per_capita <- mean(provincial_vaccine_comparisons_last_date$administered_doses_per_capita)

cat(paste("Mean: ", mean_administered_doses_per_capita))

```








```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

# This just adds a blank row to the table for the median/mean labels on the graphic
# provincial_vaccine_comparisons_last_date <- provincial_vaccine_comparisons_last_date %>%
#   add_row(
#   date                          = as.Date("2021-04-07") ,
#   province                      = " ",
#   cumulative_dvaccine           = 0 ,
#   cumulative_avaccine           = 0 ,
#   vaccination_gap_pct           = 0 ,
#   dose_difference_cnt           = 0 ,
#   population                    = 0 ,
#   administered_doses_per_capita = 0 ,
#   administration_gap_per_capita = 0 ,
#   )



p_provincial_vaccinations_per100K <- plot_bar_x_reordered_y(
  provincial_vaccine_comparisons_last_date,
  x_var=province, y_var=administered_doses_per_capita,
  bar_colour = nominalMuted_shade_0,
  title_str="Provincial COVID-19 vaccinations per capita",
  subtitle="Vaccinations per 100,000 people age 18 or older. Includes first and second doses",
  y_units="", ymin=0, ymax=100000,
  source_str="COVID-19 CANADA OPEN DATA WORKING GROUP", lastupdate_str=last_update_timestamp
)

p_provincial_vaccinations_per100K <- p_provincial_vaccinations_per100K +
  geom_hline(yintercept = median_administered_doses_per_capita, linetype="dotted",
                color = "#222222", size=.35)  +
  annotate("text",
             x = " ",
             y = median_administered_doses_per_capita,
             label = wrap_text(paste(
               "Median ", comma(median_administered_doses_per_capita), "/100K people",
               "\n",
               "Mean ", comma(mean_administered_doses_per_capita), "/100K people",
               sep=""
               ), 27),
             size=3, hjust=-.09,
             colour = "#000000"
    )

wfp_provincial_vaccinations_per100K <- prepare_plot(p_provincial_vaccinations_per100K)
ggsave_pngpdf(wfp_provincial_vaccinations_per100K, "wfp_provincial_vaccinations_per100K", width_var=8.66, height_var=6, dpi_var=96, scale_var=1, units_var="in")

plot(wfp_provincial_vaccinations_per100K)


# p_provincial_vaccinations_per100K <-  ggplot(provincial_vaccine_comparisons_last_date) +
#  aes(x = reorder(province, administered_doses_per_capita), weight = administered_doses_per_capita) +
#  geom_bar(
#           fill =nominalMuted_shade_0) +
#  # geom_bar(
#  #          data=provincial_vaccine_comparisons_last_date %>% filter(province=="Manitoba"),
#  #          aes(x = reorder(province, administered_doses_per_capita), weight = administered_doses_per_capita),
#  #          fill =wfp_blue) +
#  #  geom_text(data=provincial_vaccine_comparisons_last_date,
#  #    aes(x = reorder(province, administered_doses_per_capita), y = 0, label=comma(administered_doses_per_capita, accuracy=2)), size=3, hjust=-.35, colour="#ffffff"
#  #  ) +
#   geom_hline(yintercept = median_administered_doses_per_capita, linetype="dotted",
#                 color = "#222222", size=.35)  +
#   # geom_hline(yintercept = mean_administered_doses_per_capita, linetype="dashed",
#   #               color = "#222222", size=.35)  +
#   annotate("text",
#              x = " ",
#              y = median_administered_doses_per_capita,
#              label = wrap_text(paste(
#                "Median ", comma(median_administered_doses_per_capita), "/100K people",
#                "\n",
#                "Mean ", comma(mean_administered_doses_per_capita), "/100K people",
#                sep=""
#                ), 27),
#              size=3, hjust=-.09,
#              colour = "#000000"
#     ) +
#     scale_y_continuous(
#     expand = c(0, 0),
#     limits=c(0, 100000),
#     breaks=seq(0,100000,by=25000),
#     label=comma
#   ) +
#   coord_flip()+
#  labs(
#     title = "Provincial COVID-19 vaccinations per capita",
#     subtitle="Vaccinations per 100,000 people age 18 or older. Includes first and second doses",
#     caption = paste("WINNIPEG FREE PRESS — SOURCE: COVID-19 CANADA OPEN DATA WORKING GROUP (2021-04-08)", sep = ""),
#     x = "",
#     y = ""
#   ) +
#  minimal_theme() +
#     theme(
#       axis.line=element_blank(),
#       # axis.text.x=element_blank(),
#       # axis.ticks=element_blank(),
#       axis.title.x=element_blank(),
#       panel.grid.major.y=ggplot2::element_blank(),
#       panel.grid.minor.y=ggplot2::element_blank()
#     )
#



```



----


## Data tables


### Daily first and second doses as reported by Manitoba Health
**Daily vaccinations numbers lag by several days because of data inputting delays. Daily changes in the cumulative totals does not reflect daily vaccinations**
```{r table_COVID19_MB_first_second_vaccine_dose, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(COVID19_MB_first_second_vaccine_dose,
          caption = 'Table: COVID19_MB_first_second_vaccine_dose',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 10,
            order = list(list(0, 'desc'))
          ))

```
----

### Provincial vaccination comparison
** As reported by provinces. Data compiled by COVID-19 Canada Open Data Working Group**
```{r , echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, results="asis", collapse = TRUE}

datatable(provincial_vaccine_comparisons,
          caption = 'Table: provincial_vaccine_comparisons',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 10,
            order = list(list(0, 'desc'))
          )
)

```

----

### Population projections

**Population estimates on July 1st, by age and sex**

Statistics Canada produces annual populations, by age group and sex, for a July 1 projection.  Lenore K., from provincial comms, provided the population of Manitobans eligible for the vaccine (18+) based on a December 2020 projection by Manitoba's Bureau of Statistics. The MBBoS population matches the July 1 figure provided by Statistics Canada.

[Table: 17-10-0005-01 | Population estimates on July 1st, by age and sex](https://www150.statcan.gc.ca/t1/tbl1/en/cv!recreate.action?pid=1710000501&selectedNodeIds=3D101&checkedLevels=0D1,0D2,1D1&refPeriods=20200101,20200101&dimensionLayouts=layout3,layout2,layout2,layout2&vectorDisplay=false)



```{r viz_tbl_populations, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8.66, fig.height=6, collapse = TRUE}

population_provinces_2020_all_18plus <- left_join(
  population_provinces_2020,
  population_provinces_18plus_2021Q2,
  by=c("province"="province")
) %>%
  select(
    "province",
    "population.x",
    "population.y"
  ) %>%
  rename(
    "population_full" = "population.x",
    "population_18plus" = "population.y"
  )

datatable(population_provinces_2020_all_18plus,
          caption = 'Table: population_provinces_2020_all_18plus',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 15,
            order = list(list(0, 'desc'))
          ))



datatable(mbhealth_population_agegroups_12plus,
          caption = 'Table: mbhealth_population_agegroups_12plus',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 15,
            order = list(list(0, 'desc'))
          ))

datatable(mbhealth_population_agegroups,
          caption = 'Table: mbhealth_population_agegroups',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 15,
            order = list(list(0, 'desc'))
          ))

datatable(mbhealth_population_age_20200601,
          caption = 'Table: mbhealth_population_age_20200601',
          class="cell-border stripe", rownames=FALSE,
          options = list(
            pageLength = 15,
            order = list(list(0, 'desc'))
          ))

```



